A Language's Unigram Entropy Distribution Predicts Self-Paced Reading Times [Rewrite title]

### 2019-01-15 cogsci/position-info.Rmd
Cogsci edits to-do list

---
title: "A Language's Unigram Entropy Distribution Predicts Self-Paced Reading Times"
bibliography: library.bib
csl: apa6.csl
document-params: "10pt, letterpaper"

@@

abstract: 
    "A major line of research in the cognitive sciences has asked how speakers and writers distribute information in the linguistic material they produce. We provide evidence against the Uniform Information Density hypothesis (Jaeger, 2010) which proposes that information is transmitted at a constant rate close to channel capacity in human communication. We instead argue that the information structure and transmission rate in human communication varies predictably from language to language based on phonological and syntactic features. We draw evidence from written and spoken corpora, including corpora of parent and child communication at various ages and large-scale online corpora from Wikipedia in a typologically diverse collection of languages."

@@

How do people convey information in speech and text? Is there a regular distribution to how information is conveyed across speech and text? Does speech, with its phonological properties, different from writing, with its semiotic properties, in how information is conveyed?

@@

Jaeger (2010) extends the CER principle to all levels of human communication: the *Uniform Information Density* (UID) hypothesis. Jaeger argues that speakers will try to distribute information more evenly over the course of an utterance, to be as close to channel capacity (in a Shannon sense) as possible. In particular, Jaeger singles out the production of "that" at the beginning of relative clauses in English and the use of contractions such as "he's" and "you're" versus "he is" and "you are" as instances where higher information density in the clause elicits the production of more material by speakers.

@@

To explore information transmission rate in speech, we used the CHILDES TalkBank (Brown 1973; MacWhinney 2000) corpora database of spoken adult-child conversations. We first used the Brown and Providence English corpora from CHILDES. The Brown corpus contains individual recordings of conversations between three children between 1.5 and 6-years-old and their families in their homes. The Providence corpus recorded interactions between children between 1 and 3 years old and their parents in the home. We divided each corpus by speaker into child and non-child categories. We further divided the corpora by utterance length, so that all sentences of length $k$ (e.g. $6$) were grouped together. Finally, within each utterance length, we computed the unigram entropy measure for each position. We follow Yu et al. (2016) in using the following formula for each word position X of sentences of fixed length k from the corpus, where each $w$ is a word occurring in position $X$ and $p(w)$ is the number of times word $w$ occurs in position X divided by the number of total words that occur in position $X$ i.e. the number of sentences of length $k$.

@@

# Results & Analysis
The Unigram Information Density account would predict that children have a lower channel capacity for communication and would instead communicate with a less unigram entropy curve. The adult and child entropy curves track one another almost identically. This not only indicates a robustness in the unigram entropy curve across speakers, but also across ages and addressees. We also observed a robustness across corpora for the same languages, and a robustness across utterance lengths within the same corpus's entropy curve. This shows that the concept of an "entropy curve" for a specific language is well-founded when considering speech data.

@@

# Large-scale text data
We also wanted to apply this analysis to large-scale text data, to compare with the parent-child speech data results from using CHILDES. Using Giuseppe Attardi's Wikiextractor tool \footnote{https://github.com/attardi/wikiextractor}, we extracted the text corpora for $165$ languages from Wikipedia by downloading a stored collection of Wikipedia entries in each langauge and randomly selecting several thousand articles from each Wikipedia language. Each language corpus was cleaned and limited to sentences between $6$ and $50$ words. Similar to the data from CHILDES, we divided each corpus by sentence length, and then computed the unigram entropy measure on each word position within each sentence length.

@@

>>>>

---
title: "A Language's Unigram Entropy Distribution Predicts Self-Paced Reading Times [Rewrite title]"
bibliography: library.bib
csl: apa6.csl
document-params: "10pt, letterpaper"

@@

abstract: 
    "A major line of research in the cognitive sciences has asked how speakers and writers distribute information in the linguistic material they produce [include citations here or rewrite this paragraph]. We provide evidence against the Uniform Information Density hypothesis (Jaeger, 2010) which proposes that information is transmitted at a constant rate close to channel capacity in human communication [Why does it matter that this is the hypothesis we are arguing against]. We instead argue that the information structure and transmission rate in human communication varies predictably from language to language based on phonological and syntactic features. We draw evidence from written and spoken corpora, including corpora of parent and child communication at various ages and large-scale online corpora from Wikipedia in a typologically diverse collection of languages [Rewrite final sentence for clarity]."

@@

How do people convey information in speech and text? Is there a regular distribution to how information is conveyed across speech and text? Does speech, with its phonological properties, different from writing, with its semiotic properties, in how information is conveyed? [Are we pitting speaking against writing?]

@@

Jaeger (2010) extends the CER principle to all levels of human communication: the *Uniform Information Density* (UID) hypothesis. Jaeger argues that speakers will try to distribute information more evenly over the course of an utterance, to be as close to channel capacity (in a Shannon sense) as possible. In particular, Jaeger singles out the production of "that" at the beginning of relative clauses in English and the use of contractions such as "he's" and "you're" versus "he is" and "you are" as instances where higher information density in the clause elicits the production of more material by speakers [Explain the Jaeger data more clearly and succintly, connect with other examples in the literature more broadly].

@@

To explore information transmission rate in speech, we used the CHILDES TalkBank (Brown 1973; MacWhinney 2000) corpora database of spoken adult-child conversations [Why does it matter to examine child vs adult data]. We first used the Brown and Providence English corpora from CHILDES. The Brown corpus contains individual recordings of conversations between three children between 1.5 and 6-years-old and their families in their homes. The Providence corpus recorded interactions between children between 1 and 3 years old and their parents in the home. We divided each corpus by speaker into child and non-child categories. We further divided the corpora by utterance length, so that all sentences of length $k$ (e.g. $6$) were grouped together. Finally, within each utterance length, we computed the unigram entropy measure for each position. We follow Yu et al. (2016) in using the following formula for each word position X of sentences of fixed length k from the corpus, where each $w$ is a word occurring in position $X$ and $p(w)$ is the number of times word $w$ occurs in position X divided by the number of total words that occur in position $X$ i.e. the number of sentences of length $k$. [Give the equation its own paragraph]

@@

# Results & Analysis
The Unigram Information Density account would predict that children have a lower channel capacity for communication and would instead communicate with a less unigram entropy curve. The adult and child entropy curves track one another almost identically [Make this contrast with the prediction stronger, introduce . This not only indicates a robustness in the unigram entropy curve across speakers, but also across ages and addressees. We also observed a robustness across corpora for the same languages, and a robustness across utterance lengths within the same corpus's entropy curve. This shows that the concept of an "entropy curve" for a specific language is well-founded when considering speech data.

@@

# Large-scale text data [Why does this comparison matter?]
We also wanted to apply this analysis to large-scale text data, to compare with the parent-child speech data results from using CHILDES. Using Giuseppe Attardi's Wikiextractor tool \footnote{https://github.com/attardi/wikiextractor}, we extracted the text corpora for $165$ languages from Wikipedia by downloading a stored collection of Wikipedia entries in each langauge and randomly selecting several thousand articles from each Wikipedia language. Each language corpus was cleaned and limited to sentences between $6$ and $50$ words. Similar to the data from CHILDES, we divided each corpus by sentence length, and then computed the unigram entropy measure on each word position within each sentence length.

@@

## Flora's feedback: 
1. Extend the background section with more information about the literature (what are some of the consequence of the unigram entropy, where has this been applied). 
2. Talk about the speech and text distinction in the literature and how that affects your work. 
3. Talk about how your work looks at multiple languages (has this been done before). 
4. Talk more about child versus adult distinction. 
6. Talk more about entropy in general, and then why this measure applies to this work (Genzel and Charniak?). 
7. Have a method and results section (i.e. clearer division) with both the CHILDES and the Wikipedia data.
## Self feedback:
1. Motivating sections and why you chose the corpora you did
2. Clean up and rerun Wikipedia code
3. Write WALS features section. Why do we care about the typological features? 
4. Write clustering section and section about what features matter explored using statistical modeling. 
5. Spinal column: Why does information structure through entropy matter? How has it impacted the literature (Genzel & Charniak, Hale, Levy, Piantadosi, etc.)? Why does UID matter? What does the stuff we do here show? Why do we choose the particular corpora, entropy methods and analyses we do? How does this potentially connect with eye-tracking and sentence processing in general?
